MLCommons Earthquake Science Benchmark

### 2022-01-30 paper-capstone-earthquake.tex
recover refernces, remove acm template

\documentclass[sigplan,screen]{acmart}
\usepackage{todonotes}

@@

\setcopyright{acmcopyright}
\copyrightyear{2022}
\acmYear{2022}
\acmDOI{XXXXXXX.XXXXXXX}

\acmConference[Conference acronym 'XX]{Make sure to enter the correct
  conference title from your rights confirmation emai}{June 03--05,
  2018}{Woodstock, NY}
%\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
%  June 03--05, 2018, Woodstock, NY} 
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}
%%\acmSubmissionID{123-A56-BU3}
%%\citestyle{acmauthoryear}

@@

\author{Robert Knuuti}
\affiliation{%
  \institution{University of Virginia}
  \streetaddress{TBD}
  \city{Charoletteville}
  \country{USA}}
\email{uqq5zz@virginia.edu}

@@

@@

@@

@@

Things to do: 
\begin{itemize}
    %\item add presentation as cite,
    \item Review IEEE Presentation \cite{fox2022aiforscience}
    \item Review MLCommons \cite{www-mlcommons} 
    \item Use jabref \cite{www-jabrefg-org} for citation management
    \item Review Fox paper \cite{fox2021earthquake}
    \item Frequently check github \cite{www-mlcommons-eathquake}
    \item Read up on TFT \cite{www-onnen2021}
    \item Become familiar with the Attention Paper \cite{vaswani2017attention}
    \item Learn how to selfdeploy jupyterlab \cite{www-jupyterlab}
    \TODO{Is this the same as jupytext?}

@@

UVA, Rivanna, A100, RTX3090, others may not have enough memory. 
\TODO{description of Rivanna on web page is not accurate.}

\subsection{Rutherfordlab ???}
\label{id:ral}

Rutherfordlab (RAL)

@@

Oak Ridge National Labratory (ORNL), Summit

\subsection{NERSC ???}
\label{id:nersc}

National Energy Research Scientific Computing Center (NERSC), ...

@@

Argonne National Laboratory (ANL), ...

@@

San Diego Super Computing Center, ...

@@

\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:my_label}
    \centering
    \begin{tabular}{|r|l|l|r|l|l|l|}
        \hline
        Section & Organization & Machine  & Processors & GPUs & GPU Type  & Commissioned \\ 
        \hline
        \hline
         \ref{id:uva}   & UVA       & Rivanna   &            &      &           & \\
         \ref{id:ral}   & RAL       &           &            &      &           & \\
         \ref{id:ornl}  & ORNL      &  Summit   &            &      &           & \\
         \ref{id:nersc} & NERSC     &           &            &      &           & \\
         \ref{id:anl}   & ANL       &           &            &      &           & \\
         \ref{id:sdsc}  & SDSC      &           &            &      &           & \\
         \ref{id:dgx}   & DGX Staion A100   &           & 1          &  AMD EPYC 7742 64-Core Processor   & A100 80GB  & Fox will know\\
         \hline
    \end{tabular}
\end{table*}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{references,sample-base}

@@

\TODO{Not sure if we want to talk about building tasks / kanban boards to track the different parts of work we'll be doing each week.  Additionally, it might be good to decide on some core roles to make sure things don't fall through the cracks (roles like recorder, scheduler, reviewer, et al...); the non-technical stuff for now, and then we can get into the more specific things once we pass the initial knowledge rampup}

>>>>

\documentclass[sigplan,screen]{format/acmart}
\usepackage{todonotes}
\usepackage{graphicx}
\usepackage{wrapfig}

@@

%\setcopyright{acmcopyright}
\setcopyright{Apachee 2.0}
\copyrightyear{2022}
\acmYear{2022}
\acmDOI{XXXXXXX.XXXXXXX}

\acmConference[University of Virginia Data Science Capstone 2022]{MLCommons Earthquake Science Benchmark}{Jan. 22 -- Aug. ??,
  2022}{Charlotsville, VA}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection,
  June 03--05, 2018, Woodstock, NY} 
\acmPrice{0.00}
\acmISBN{TBD}
%%\acmSubmissionID{123-A56-BU3}
%%\citestyle{acmauthoryear}

@@

\author{Robert Knuuti}
\orcid{0000-0003-2614-0899}
\affiliation{%
  \institution{University of Virginia}
  \streetaddress{TBD}
  \city{Charoletteville}
  \country{USA}}
\email{robert.knuuti@gmail.com}

@@

\author{Judy Fox}
\affiliation{%
  \institution{University of Virginia}
  \streetaddress{TBD}
  \city{Charlotsville, VA}
  \country{USA}}
\email{cwk9mp@virginia.edu}

@@

Several research efforts have been executed over the years to establish a set of leading factors that could be used to predict where an earthquake could occur.
Not only is this an algorithmically complex problem, but it is also computationally difficult to perform\cite{fox2022aiforscience}.
The intersection of these two elements create an ideal environment for building benchmarks.
By establishing a rigorous process to build a repeatable models, we can establish a benchmark to not only measure the performance of high performance supercomputers, but also take steps to building a stronger understanding of what models perform best to predict when and earthquake could occur.

For this study, we review the following models across various hardware platforms to establish this benchmark:
\begin{itemize}
    \item pure (vanilla) recurrent neuronetwork
    \item spacio-temporal science transformer
    \item temporal fusion transformer
\end{itemize}

@@

MLCommons is an open engineering organization that seeks to unify the engineering and machine learning communities through system benchmarks, open data, and best practices\ref{www-mlcommons}.
By using open data, a reference implementation for benchmarking, and executing best practices, you can build the necessary rigor to construct repeatable research to establish a basis when performing future analysis.

This organization will establish the dimensions for what is the minimally viable solution and to establish our comparison criteria across our models and the executions on the different hardware sets.

\TODO{Need to confirm what the criteria of the benchmark submission is.}

@@

Things to do:

\begin{itemize}
    %% \item add presentation as cite,
    \item Review IEEE Presentation \cite{fox2022aiforscience}
    \item Review MLCommons \cite{www-mlcommons} 
    \item Use jabref \cite{www-jabrefg-org} for citation management
    \item Review Fox paper \cite{fox2021earthquake}
    \item Frequently check github \cite{www-mlcommons-eathquake}
    \item Read up on TFT \cite{www-onnen2021}
    \item Become familiar with the Attention Paper \cite{vaswani2017attention}
    \item Learn how to selfdeploy jupyterlab \cite{www-jupyterlab}
    \TODO{Is this the same as jupytext?}

@@

UVA, Rivanna, A100, RTX3090, others may not have enough memory. 
\cite{www-rivanna}
\TODO{description of Rivanna on web page is not accurate.}

\subsection{Pearl}
\label{id:ral}

Rutherford Appleton Laboratory (RAL), UK 
Pearl \cite{www-pearl-1}

@@

Oak Ridge National Labratory (ORNL), Summit \cite{www-summit}

\subsection{Perlmutter}
\label{id:nersc}

National Energy Research Scientific Computing Center (NERSC), ...
\cite{www-perlmutter}

@@

Argonne National Laboratory (ANL), ... \cite{www-aurora}

@@

San Diego Super Computing Center, ... \cite(www-expanse}

@@

\begin{table*}[htb]
    \caption{Overview of compute resources.}
    \label{tab:my_label}
    \centering
    \begin{tabular}{|r|l|l|r|l|l|}
        \hline
        Section & Organization & Machine  & Processors & GPUs &  Commissioned \\ 
        \hline
        \hline
         \ref{id:anl}   & ANL       &  Aurora \cite{www-aurora}         &            &      &    ??? 2022       \\
         \ref{id:ornl}  & ORNL      &  Summit \cite{www-summit}  &  27000  & NVIDIA Volta GPUs    &            \\
         \ref{id:nersc} & NERSC     &  Perlmutter \cite{www-perlmutter}         &    6000    & NVIDIA A100 & Jan 2022        \\
         \ref{id:sdsc}  & SDSC      &  Expanse \cite{www-expanse}         & 200&     NVIDIA V100 SMX2     &            \\
         \ref{id:uva}   & UVA       & Rivanna \cite{www-rivanna}  &      8       & NVIDIA A100 80GB     & Feb 2022 \\
         \ref{id:ral}   & RAL       &  Pearl \cite{www-pearl-1}        &   16         &  NVIDIA V100   &            \\
         \ref{id:dgx}   & Fox & DGX Staion A100 \cite{www-dgx-station-a100}  & 4 &  NVIDIA A100 80GB  & May 2021\\
         \hline
    \end{tabular}
\end{table*}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\section*{Biographies}

\TODO{wrapfigure does somehow not work in this template}

{\bf Thomas Butler}
\TODO{Thomas: fill out. See Gregor's example}

{\bf Robert Knuuti}
is a Graduate Student at University of Virginia's School of Data Science. He has over 10 years experience in system architecture and software engineering, and specializes in Development Operations and Cloud Computing. \TODO{Not sure what to add about research organizations; I'm generally not affiliated.}  He has constructed air gapped Continuous Integration and Continuous Delivery systems for multiple organizations each supporting more than 100 developers and has facilitated the construction of repeatable, tractable builds for users of these systems.

{\bf Jake Kolessar}
\TODO{Jake: fill out. See Gregor's example}

{\bf Geoffrey C. Fox}
\TODO{Geoffery: fill out}

%\begin{wrapfigure}{r}{0.25\columnwidth}
%\includegraphics[width=0.24\columnwidth]{images/bio/gregor.png}
%\end{wrapfigure}

{\bf Gregor von Laszewski}
is a Research Professor at University of Virginia. He has more than 30 years of experience in parallel and distributed computing. Selected research organizations he worked in include NASA, Argonne National Laboratory, Indiana University. He is proud to have been contributing members of researchteams that invented hybrid parallel genetic algorithms, Grid computing, and the first large scale academic hybrid cloud, as well as the larges scientific bibliometric analysis of XSEDE in the world.

@@

\TODO{Not sure if we want to talk about building tasks / kanban boards to track the different parts of work we'll be doing each week.  Additionally, it might be good to decide on some core roles to make sure things don't fall through the cracks (roles like recorder, scheduler, reviewer, et al...); the non-technical stuff for now, and then we can get into the more specific things once we pass the initial knowledge rampup}
\TODO{We now have a project board for this semester, milestones, and issues.}
